Exploring Bounds

### 2015-04-24 draft.tex
figured out lexicode proof

We have used the idea of nim-sums and zero-sums throughout the course, but instead we have
referred to this notion in terms being even-like or odd-like.  This is the
exact same notion, only in different terms.

@@

\begin{proof}
We will prove this by inducting on $n$.  In the base case of $n=1$,
$\mathcal{L}=\{0\}$, which is trivially zero-sum.  Assume that for the
lexicode of length $n$, which we will denote $\mathcal{L}(n)$, all codewords are zero-sum.  Now, we must show that all
the codewords in $\mathcal{L}(n+1)$ are zero-sum as well.  First, note that all
codewords in $\mathcal{L}(n)$ are also in $\mathcal{L}(n+1)$, except with an
extra leading zero.  By our assumption, these codewords are still zero-sum, as
adding a zero in front will not change the nim-sum calculation.
Now, we must show that any vector we can add to this set as proscribed by our
algorithm must necessarily be a zero-sum vector as well.
\end{proof}

>>>>

We have used the idea of nim-sums and zero-sums throughout the course, but instead we have
referred to this notion in terms of being even-like or odd-like.  This is the
exact same notion, only in different terms.

@@

\begin{proof}
We will prove this by inducting on $n$.  In the base case of $n=1$,
$\mathcal{L}=\{0\}$, which is trivially zero-sum.  Assume that for the
lexicode of length $n$, which we will denote $\mathcal{L}(n)$, all codewords are zero-sum.  Now, we must show that all
the codewords in $\mathcal{L}(n+1)$ are zero-sum as well.  First, note that all
codewords in $\mathcal{L}(n)$ are also in $\mathcal{L}(n+1)$, except with an
extra leading zero.  By our assumption, these codewords are still zero-sum, as
adding a zero in front will not change the nim-sum calculation.
Now, we must show that any vector we can add to this set as prescribed by our
algorithm must necessarily be a zero-sum vector as well.

Since $\mathcal{L}(n)$ is contained in $\mathcal{L}(n+1)$, we begin our construction of $\mathcal{L}(n+1)$ with the elements of $\mathcal{L}(n)$.  Any new elements
we will add must have a $1$ in the leading coordinate as we have maxed out our possibilities for $\mathcal{L}(n)$, and so lexicographically this makes sense as the new vectors we now need to consider will be `larger' than the ones
we have already added in to $\mathcal{L}(n+1)$.

-If you approach an odd-weight vector that you can add, then there is even-weight vector that comes one before it that you should have added instead.

-SHIT! if it is odd weight, then by definition that means that has a 1 in the leading column plus an even weight vector from $\mathcal{L}(n)$!!!!  That vector must necessarily be 
distance 1 away from a vector in $\mathcal{L}(n)$, and thus cannot be added to $\mathcal{L}(n+1)$.  All even weight vectors will have a $1$ in the leading coordinate and then
an odd number of $1$s in the next $n$ coordinates.  No odd numbers are in $\mathcal{L}(n)$, and so you will be at least distance one from all vectors already from $\mathcal{L}(n)$.
So you get one component of your distance from the leading coordinate and at least one component of distance from you the last $n$ coordinates.  This completes the 
proof!
\end{proof}
